Supervised Dimensionality Reduction with Random Projection-Based Ensemble Learning

### 2021-02-17 main.tex

\begin{figure}[htbp]
\centering
\includegraphics[width=4in]{figures/ExampleFigures.png}
\caption{Simple distributions that will provide a range of challenges to clustering and/or variable selection methods when embedded in higher dimensional space.\label{fig:examplefigures}}
\end{figure}

@@

\[
X \perp\!\!\!\perp Y\ | \ AX
\]
where $A$ being a projection mandates that $A {A}^T = I_d$. The sufficient subspace determined by $A$, which we denote $V(A)$, is given by the column space $\text{col}(A^TA)$.
\end{definition}
The notion of a sufficient subspace is a special case of the more general sufficient dimension reduction condition. This requires only a function $S:\mathbb{R}^p\rightarrow \mathbb{R}^d$ such that $X \perp\!\!\!\perp Y\ | \ S(X)$. A sufficient subspace exists if $S$ can be chosen to be linear.

We may immediately see that all joint distributions $(X,Y)$ admit a sufficient subspace (namely via the identity map $A= I_p$). Furthermore, any superspace $W \supseteq V$ of a sufficient subspace $V$ is also sufficient. While it is not necessarily true that the intersection $V_1 \cap V_2$ of two sufficient subspaces $V_1,V_2$ is itself sufficient, \citet[Lemma 2]{cook_graphics_1996} laid out conditions under which this is the case which are broad enough for our purposes. Under such circumstances it makes sense to discuss the central subspace 
\begin{equation*}
    C_{Y|X} := \cap_{V: V\text{ sufficient}}V.
\end{equation*}
A variety of methods for estimation of the central subspace have been proposed. Several have proceeded by maximising an estimate of the dependence between $AX$ and $Y$, where the dependence is measured by log-loss mutual information \citep{torkkola_feature_2003, suzuki_approximating_2008}, squared-loss mutual information \citep{suzuki_sufficient_2012, yamada_sufficient_2011}, or distance correlation \citep{vepakomma_supervised_2018}. Related to the notion of the central subspace is that of the central mean subspace,introduced in \citet{cook_dimension_2002} along with a discussion of methods for its estimation. In the case of binary classification, which we will consider, the central subspace and central mean subspace are equivalent. Therefore, work geared towards estimation of the central mean subspace \citep[see for example][]{ma_estimation_2014} is also within our purview.\\

@@

\begin{figure}
    \centering
    \includegraphics[width=5in]{figures/sim1_ev.png}
    \caption{Caption}
    \label{fig:sim1_ev}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/sim2_ev.png}
    \caption{Caption}
    \label{fig:sim2_ev}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/sim3_ev.png}[]
    \caption{Caption}
    \label{fig:sim3_ev}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics{figures/sim4_ev.png}
    \caption{Caption}
    \label{fig:sim4_ev}
\end{figure}

>>>>

\begin{figure}[htbp]
    \centering
    \includegraphics[width=4in]{figures/ExampleFigures.png}
    \caption{\textbf{A}: Component-aligned, axis-aligned; \textbf{B}: Not component-aligned, axis-aligned;\textbf{C}: Component-aligned, not axis-aligned;\textbf{D}: Not component-aligned, not axis-aligned.\label{fig:examplefigures}}
\end{figure}

@@

    \[
    X \perp\!\!\!\perp Y\ | \ AX
    \]

    where $A$ being a projection mandates that $A {A}^T = I_d$. The sufficient subspace determined by $A$, which we denote $V(A)$, is given by the column space $\text{col}(A^TA)$.
\end{definition}

The notion of a sufficient subspace is a special case of the more general sufficient dimension reduction condition. This requires only a function $S:\mathbb{R}^p\rightarrow \mathbb{R}^d$ such that $X \perp\!\!\!\perp Y\ | \ S(X)$. A sufficient subspace exists if $S$ can be chosen to be linear.

We may immediately see that all joint distributions $(X,Y)$ admit a sufficient subspace (namely via the identity map $A= I_p$). Furthermore, any superspace $W \supseteq V$ of a sufficient subspace $V$ is also sufficient. While it is not necessarily true that the intersection $V_1 \cap V_2$ of two sufficient subspaces $V_1,V_2$ is itself sufficient, \citet[Lemma 2]{cook_graphics_1996} laid out conditions under which this is the case which are broad enough for our purposes. Under such circumstances it makes sense to discuss the central subspace

\begin{equation*}
    C_{Y|X} := \cap_{V: V\text{ sufficient}}V.
\end{equation*}

A variety of methods for estimation of the central subspace have been proposed. Several have proceeded by maximising an estimate of the dependence between $AX$ and $Y$, where the dependence is measured by log-loss mutual information \citep{torkkola_feature_2003, suzuki_approximating_2008}, squared-loss mutual information \citep{suzuki_sufficient_2012, yamada_sufficient_2011}, or distance correlation \citep{vepakomma_supervised_2018}. Related to the notion of the central subspace is that of the central mean subspace,introduced in \citet{cook_dimension_2002} along with a discussion of methods for its estimation. In the case of binary classification, which we will consider, the central subspace and central mean subspace are equivalent. Therefore, work geared towards estimation of the central mean subspace \citep[see for example][]{ma_estimation_2014} is also within our purview.\\

@@

\begin{figure}
    \centering
    \includegraphics[width=6in]{figures/sim1_ev.png}
    \caption{Caption}
    \label{fig:sim1_ev}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=6in]{figures/sim2_ev.png}
    \caption{Caption}
    \label{fig:sim2_ev}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=6in]{figures/sim3_ev.png}[]
    \caption{Caption}
    \label{fig:sim3_ev}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=6in]{figures/sim4_ev.png}
    \caption{Caption}
    \label{fig:sim4_ev}
\end{figure}
